Introduction to data

### 2018-09-01 DATA606/Lab1/michael-intro_to_data.Rmd
Work on DATA 606 Lab 1

```{r}
library(e1071)
summary(wdiff)
skewness(wdiff)
```

@@

**The data is left skewed and clustered around -10 to -15.  There is a few extreme values but in generall people want to loose a few pounds.**

@@

```{r}

```

@@

>>>>

```{r}
summary(wdiff)

library(e1071)
skewness(wdiff)
```

@@

**The data is left skewed and clustered around -10 to -15.  There is a few extreme values but in general people want to loose a bit of weight.**

@@

```{r}
cdc$wdiff <- cdc$wtdesire - cdc$weight
summary(cdc[cdc$gender == "m",]$wtdesire)
summary(cdc[cdc$gender == "f",]$wtdesire)

boxplot(cdc$wtdesire ~ cdc$gender)
```

**In order to see how they different genders viewed their weight I decided to look at the weight they desired.  It would stand as a proxy for the "ideal" man or woman.  As one would expect the "ideal" male's weight is heavier than the "ideal" female's.**

@@

```{r}
mu <- mean(cdc$weight)
mu
sigma <- sd(cdc$weight)
sigma

upper <- mu + sigma
lower <- mu - sigma

nrow(cdc[cdc$weight>=lower & cdc$weight<=upper,]) / nrow(cdc)
```

**The mean is roughly 170 with a standard deviation of about 40.  About 71% are within one standard deviation of the mean.**
